Making multiple-locus association mapping on a genome-wide scale routine

### 2017-10-31 AM+draft.tex
31Oct17 end of day updates

Glmnet is a general purpose R package for statistical analysis. It implements elastic net regression, 
a regularisation method that has been applied to generalised linear models \cite{zou2005regularization}.   
Glmnet was not specifically built for association mapping. However, we included it amongst the applications to benchmark 
Eagle against because of the interest surrounding its use for analysing data from genetic
studies \cite{cho2010joint,huang2015empirical}.  The regression model we used for analysis is 
$y = X \beta + \sum_{l=1}^L m_l \theta_l + e$ where $\theta_l; l=(1,2, \ldots, L)$ is the coefficient for the $l$th snp. 
Elastic net allows us to obtain parameter estimates from this model via a penalty function that is a mixture of 
$\ell_1$ (lasso) and $\ell_2$ (ridge regression).

>>>>

Glmnet is a general purpose R package for regression analysis. It implements elastic net, 
a regularisation method where the penalty function 
is a mixture of 
$\ell_1$ (lasso) and $\ell_2$ (ridge regression) normalisation  \cite{zou2005regularization}. 
This allows elastic net to avoid the limitations of lasso (ref) 
while still being able to perform shrinkage and variable selection, simultaneously. 
Glmnet was not specifically built for association mapping. 
However, it is included in our list of comparison applications due to its solid performance for genomic prediction (refs).
The model upon which our analyses are based is 
$y = X \beta + \sum_{l=1}^L m_l \theta_l + e$ where $\theta_l; l=(1,2, \ldots, L)$ is the coefficient for the $l$th snp. 
The glmnet package 
implements a modification of the LARS algorithm \cite{efron2004least} for finding the optimal regularisation (solution) path. 
However, from exploratory analyses of the simulated data, we found this algorithm yielded a high proportion of false positives. 
We instead fixed the shrinkage parameter to a suitable value 
and employed stability selection to estimate the significance of the snp coefficients, empirically (see below).

we included it amongst the applications to benchmark 
Eagle against because of the interest surrounding its use for analysing data from genetic
studies \cite{cho2010joint,huang2015empirical}.  The regression model we used for analysis is 
$y = X \beta + \sum_{l=1}^L m_l \theta_l + e$ where $\theta_l; l=(1,2, \ldots, L)$ is the coefficient for the $l$th snp. 
Elastic net allows us to obtain parameter estimates from this model via a penalty function that is a mixture of 
$\ell_1$ (lasso) and $\ell_2$ (ridge regression). 
The glmnet package 
implements a modification of the LARS algorithm \cite{efron2004least} for finding the optimal regularisation (solution) path. 
However, from exploratory analyses of the simulated data, we found this algorithm yielded a high proportion of false positives. 
We instead fixed the shrinkage parameter to a suitable value 
and employed stability selection to estimate the significance of the snp coefficients, empirically (see below).
